TBD

### 2021-03-05 outputs/paper/paper.Rmd
update

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

@@

## treat distribution 
```{r employee, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}

treat_map <- 
  EDA%>%
  ggplot(aes(x = EDA$treat, fill = treat)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  labs(title = "Treat distribution",x="", y="Count") +
  theme_minimal()
treat_map
```

## Age distribution

##

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
```

@@

## treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}

treat_map <- 
  EDA%>%
  ggplot(aes(x = EDA$treat, fill = treat)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  labs(title = "Treat distribution",x="", y="Count") +
  theme_minimal()

treat_map
```

## education level distribution by PID

## sexim by education level 
```{r sexim, fig.cap = "sexim by education level",echo=FALSE, fig.width=5, fig.height=4}

s1<-
  ggplot(EDA, aes(x = PID, y= ambivalent_sexism)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="sexim by education level", x="PID", y="Sexism")+
  theme_economist() + scale_fill_economist()
s1
```

## internet usage by meta.os
```{r internet, fig.cap = "internet usage by os",echo=FALSE, fig.width=5, fig.height=4}

```

## post favor by treat
